On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-07-16 documents/backup/backup_paper.tex
Quick lil citation processor
Cite processor almost done

We've got a thing 
that's called 
Radar Love
We've got a wave
in the air

The phased-array techdemo.

\paragraph{{\Large the gist}}\

The chain of literature 
%
[Fr\"{o}hlich 1968] \textrightarrow \ [Fr\"{o}hlich 1980] \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,

{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
%

estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

@@

\bibliography{flagship}

>>>>

\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]
\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]

\supercite{Yang Efficient 2016}[1789 \href{https://doi.org/10.1038/srep18030}{\faExternalLink}]

[Frolich 1968] [Frolich 1980] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conduc98 \href{https://doi.org/10.2514/3.29363}{\faExternalLink}ently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

@@

\collect{Flagship}
